---
title: "R Notebook"
output: html_notebook
---

```{r, message = FALSE, error = FALSE}
install.packages("dplyr")
install.packages("tidyverse")

library(dplyr)
library(tidyverse)
```


```{r}
PATH <- ""
smosh <- read.csv(paste(PATH, "smosh_market.csv", sep = ""))
head(smosh)
```


```{r}
smosh <- smosh %>% rename("Total Viewers" = "Total.Viewers")
sm <- ts(smosh["Total Viewers"], start = c(2022, 44), frequency = 45)
plot(sm, main = "Smosh Pit Total Weekly Total Views")
```

- Non-stationary in mean
- Dataframe only about a year, likely won't track seasonality (if any) and 
unlikely due to nature of channel
- Mild viewership jump around June 2023 (steeper slope after jump?)

```{r}
growth <- diff(sm)

which.max(growth)
growth[23]

which.min(growth)
growth[2]

# 24 and 25 (now 23 and 24) have most significant increases in viewership 
# (Anthony returns - 24th Anthony specific videos (in title))
```


```{r}
plot(growth, type = "l", main = "Smosh Pit Viewership Changes in 2023")

# 5 noticeable peaks (7, 18/19, 23/24, 32, 45)
# post big peak - different mean, variance pretty constant aside from peaks
```

- Mean more stationary...how significant is difference after massive peak
- Variance changes: some kind of seasonality or caused by outside events (like major peak)?? - appear about eqidistant of eachother


```{r}
# roa = return of Anthony

pre_roa <- growth[1:22]
post_roa <- growth[24:50]
mean(pre_roa)
mean(post_roa)
```

```{r}
plot(pre_roa, type = "l", col = "blue", ylim = c(0, 30000000), ylab = "Change in Viewership", main = "Change in Viewership Before and After Anthony's Return")
lines(post_roa, type = "l", col = "green")
points(x = c(0.3, 0.3, 0.3), c(mean(pre_roa), mean(post_roa), max(growth)), col = c("blue", "green", "black"), pch = 19)
legend(14, 30000000, legend = c("Pre-R.O.A.", "Post-R.O.A.", "Max Viewer Change"), fill = c("blue", "green", "black"))
```

Post return of Anthony has a sustained increase in viewership


```{r}
video1_len <- strcapture(".*, ([0-9]*:)*([0-9]*):([0-9]*)).*", smosh$Video.1,
                         list(hour_1 = "", minute_1 = "", second_1 = ""))
video2_len <- strcapture(".*, ([0-9]*:)*([0-9]*):([0-9]*)).*", smosh$Video.2,
                         list(hour_2 = "", minute_2 = "", second_2 = ""))
video3_len <- strcapture(".*, ([0-9]*:)*([0-9]*):([0-9]*)).*", smosh$Video.3,
                         list(hour_3 = "", minute_3 = "", second_3 = ""))
video4_len <- strcapture(".*, ([0-9]*:)*([0-9]*):([0-9]*)).*", smosh$Video.4,
                         list(hour_4 = "", minute_4 = "", second_4 = ""))

video_lengths <- cbind(video1_len, video2_len, video3_len, video4_len)
video_lengths
```

```{r}
video_lengths <- 
  video_lengths %>% 
  mutate(hour_1 = str_replace_all(hour_1, ":", ""), 
         hour_2 = str_replace_all(hour_2, ":", ""), 
         hour_3 = str_replace_all(hour_3, ":", ""), 
         hour_4 = str_replace_all(hour_4, ":", ""))

video_lengths <- data.frame(sapply(video_lengths, as.integer))

h <- c("hour_1", "hour_2", "hour_3", "hour_4")
m <- c("minute_1", "minute_2", "minute_3", "minute_4")
s <- c("second_1", "second_2", "second_3", "second_4")

video_lengths <- 
  video_lengths %>%
  rowwise() %>%
  mutate(hours = sum(c_across(any_of(h)), na.rm = TRUE),
         minutes = sum(c_across(any_of(m)), na.rm = TRUE),
         seconds = sum(c_across(any_of(s)), na.rm = TRUE)) %>%
  ungroup() %>% select("hours", "minutes", "seconds")
```


```{r}
channel_growth <- smosh %>% select(!(starts_with(("Video"))))
channel_growth["Total.Duration.of.Videos.Posted.That.Week"] <- 
  video_lengths %>%
  mutate(minutes = floor(hours*60 + minutes + seconds/60)) %>% select(minutes)
```


```{r}
channel_growth <- channel_growth[-c(1), ]
channel_growth["Viewer Growth"] <- growth[, 1]

channel_growth <- channel_growth %>% 
  relocate("Viewer Growth", .after = "Total Viewers") %>% rename(
    "Total Views of Videos Posted that Week" = Total.Views.of.Videos.Posted.that.Week,
    "Number Videos Posted" = X..Videos.Posted,
    "Avg. Views of Videos Posted that Week" = Avg..Views.of.Videos.Posted.That.Week, 
    "Total Duration of Videos Posted that Week" = Total.Duration.of.Videos.Posted.That.Week
)

rownames(channel_growth) <- NULL
channel_growth
```

```{r}
par(mfrow = c(3, 1), mar = c(2, 5, 2, 2))
ts.plot(channel_growth["Viewer Growth"], xlab = "Time", 
        ylab = "Viewer Growth")
ts.plot(channel_growth["Total Views of Videos Posted that Week"], 
        xlab = "Time", ylab = "Posted Video Views")
ts.plot(channel_growth["Total Duration of Videos Posted that Week"], 
        xlab = "Time", ylab = "Total Video Duration")
```

Viewership from the time it was measured, but average video views recorded second 
week of January, so they include all views from video posted until January 2024. 
Sometimes, peaks in viewership do not coincide with that weeks video views and 
vice versa. Videos that may have performed well at the time may not have performed 
well in comparison to other weeks.

Videos posted during Anthony's return have maintained the highest overall views 
at the time and going foreward.


Video duration consistent aside from December and January when they posted 4-9 
hour themed compilations of videos from that year.


```{r}
acf(growth, lag.max = 50)
```

MA(2)? - ACF does not appear to support white noise
- exponential decay + damped sinusoids

```{r}
pacf(growth, lag.max = 50)
```



```{r}
arima(x = growth, order = c(0, 0, 2))
arima(x = growth, order = c(1, 0, 2))
arima(x = growth, order = c(0, 0, 1))
```


Notes:
Viewers instead of subscribers
- Smosh channels old and contained many kinds of content and cast members 
(don't have accurate data for those)
- Viewership based on number of new channel views in 8 day period

8 day period instead of 7/1 week
- this was based on the way videos were posted on the channel
- 45 8 day blocks (7 days inclusive)

Use viewership changes vs total views 
- total views don't capture changes in viewership well (ie. 200,000 is a big 
jump over 8 days, but very small compared to 3mil)

Anthony usually makes appearences on Smosh main channel and Smosh Pit. 
- Pit felt more interesting to follow overtime since all the cast appears there
