---
title: "R Notebook"
output: html_notebook
---

```{r, message = FALSE, error = FALSE}
install.packages("dplyr")
library(dplyr)
```


```{r}
PATH <- ""
smosh <- read.csv(paste(PATH, "smosh_market.csv", sep = ""))
head(smosh)
```


```{r}
smosh <- smosh %>% rename("Total Viewers" = "Total.Viewers")
sm <- ts(smosh["Total Viewers"], start = c(2022, 44), frequency = 45)
plot(sm, main = "Smosh Pit Total Weekly Total Views")
```

- Non-stationary in mean
- Dataframe only about a year, likely won't track seasonality (if any) and 
unlikely due to nature of channel
- Mild viewership jump around June 2023 (steeper slope after jump?)

```{r}
growth <- diff(sm)

which.max(growth)
growth[23]

which.min(growth)
growth[2]

# 24 and 25 (now 23 and 24) have most significant increases in viewership 
# (Anthony returns - 24th Anthony specific videos (in title))
```


```{r}
plot(growth, type = "l", main = "Smosh Pit Viewership Changes in 2023")

# 5 noticeable peaks (7, 18/19, 23/24, 32, 45)
# post big peak - different mean, variance pretty constant aside from peaks
```

- Mean more stationary...how significant is difference after massive peak
- Variance changes: some kind of seasonality or caused by outside events (like major peak)?? - appear about eqidistant of eachother


```{r}
# roa = return of Anthony

pre_roa <- growth[1:22]
post_roa <- growth[24:50]
mean(pre_roa)
mean(post_roa)
```

```{r}
plot(pre_roa, type = "l", col = "blue", ylim = c(0, 30000000), ylab = "Change in Viewership", main = "Change in Viewership Before and After Anthony's Return")
lines(post_roa, type = "l", col = "green")
points(x = c(0.3, 0.3, 0.3), c(mean(pre_roa), mean(post_roa), max(growth)), col = c("blue", "green", "black"), pch = 19)
legend(14, 30000000, legend = c("Pre-R.O.A.", "Post-R.O.A.", "Max Viewer Change"), fill = c("blue", "green", "black"))
```

Post return of Anthony has a sustained increase in viewership

```{r}
acf(growth, lag.max = 50)
```

MA(2)? - ACF does not appear to support white noise
- exponential decay + damped sinusoids

```{r}
pacf(growth, lag.max = 50)
```



```{r}

```


Notes:
Viewers instead of subscribers
- Smosh channels old and contained many kinds of content and cast members 
(don't have accurate data for those)
- Viewership based on number of new channel views in 8 day period

8 day period instead of 7/1 week
- this was based on the way videos were posted on the channel
- 45 8 day blocks (7 days inclusive)

Use viewership changes vs total views 
- total views don't capture changes in viewership well (ie. 200,000 is a big 
jump over 8 days, but very small compared to 3mil)

Anthony usually makes appearences on Smosh main channel and Smosh Pit. 
- Pit felt more interesting to follow overtime since all the cast appears there
